---
title: "07. Supervised Learning - Neural Network"
author: "Liah Cha"
date: "June 27, 2017"
output: html_document
---

## Neural Networks (NN)
- AN algorithm for estimation or classification (비선형)
- Magical and mysterious hype, but just a non-linear statistical model
- Can be thought of as a generalization of regression (회귀분석의 일반화)
- "Universal approximator" 범용근사기

## Hidden Nodes
- Hidden layer nodes

- These nodes consists two parts
    + Combination function (결합함수)
    + Activation function (활성함수)
    
## Activation (Squashing) Function

1) Sigmoid(logistic), hyperbolic tangent functions
    + 미분가능함, 출력값 급격한 변화없는 S자 curve가 만들어짐 
2) Simple functions: Linear, Threshold
3) Gaussian function: RBF(Radial Basis Function) Network

- 어떤 활성함수를 쓰느냐에 따라 결과가 많이 바뀌지는 않음 기본적으로 S자 커브이기 때문 

#### Sigmoid Function

#### Tanh Function

## Output Layer Nodes

## Mathematical formuation

#### Training the Networks
- W를 발견해내는 부분 : 목적함수(예측오차)를 최소화 시키는 기준
- Training the NN menas finding a set of weights that minimize the predictive error for the records in the training set
- Many numerical methods can be used for doing this; classical one called **back propagation(역전파)**
- Back propagation recommends Quasi-Newton for medium size problems, conjugate gradient for large problems
- All suffer from stopping at local minima; common fix is to select many random starting values and save the best solution
    + 수렴하긴 하지만, global minimum이 아니라 local minimum 일 수 있음

## Cost function (목적함수)

<br/><br/>

## Example : BUYTEST
|범주 | 변수 | 변수의 내용|
|-----|-----|-----|
|인구속성|Age|나이(년)|
||Income|년수입(1000$)|
||Married|1:결혼, 0:미혼|
||Sex|F:여자, M남자|
||Ownhouse|1:소유, 0:미소유|
|지역속성|Loc|거주지(A-H)|
||Climate|거주지의 기온(10,20,30)|
|거래회수|Buy6|최근 6개월 간의 구입회수|
||Buy12|최근 12개월 간의 구입회수|
||Buy18|최근 18개월 간의 구입회수|
||Buy24|최근 24개월 간의 구입회수|
|신용상태|Fico|신용점수|
|거래속성|Orgsrc|고객분류(C,D,I,O,P,R,U)|
||Discbuy|할인고객 여부(1:할인고객, 0)|
||Return24|지난 24개월간 상품의 반품여부 (1:반품, 0)|
|응답|Respond|광고메일에 응답여부(1:응답, 0)|
||Purchtot|광고메일에 의한 구입총액|
||C1-C7|광고메일에 의한 품목별 구입액|
|고객번호|ID|고객번호|

<br/><br/>

```{r}
### Neural Network ###
buytest = read.table('./DMdata/buytest.txt',sep='\t',header=T)
head(buytest,10)
# Missing value가 하나라도 있으면 FALSE
complete=complete.cases(buytest[,c("RESPOND","AGE","FICO","BUY18")])
summary(complete) # complete 가 True 것으로만 분석 
```

```{r}
buytest1<-buytest[complete,]
nrow(buytest1)
# nor = normalization min_max (0-1사이의 범위로 변환)
nor = function(x) {(x-min(x))/(max(x)-min(x))}
buytest1$AGE <- nor(buytest1$AGE)
buytest1$FICO <- nor(buytest1$FICO)
buytest1$BUY18 <- nor(buytest1$BUY18)

# Training : Test = 5 : 5 로 분할 
set.seed(1234)
i = sample(1:nrow(buytest1), round(nrow(buytest1)*0.5)) #50% for training data, 30% for testdata
train = buytest1[i,] 
test = buytest1[-i,]
#print0('Train: ', nrow(train), ', Test: ', nrow(test))

```

```{r}
#install.packages("neuralnet",repos="http://healthstat.snu.ac.kr/CRAN/")
library(neuralnet)

set.seed(1234)
# hidden=3, 은닉층의 갯수=3개
# stepmax=10,000 iteration의 max 
# iteration 10,000번해서 수렴 못시키면 포기해라
# threshold = 0.01 : 값이 작을 수록 
# act.fct = activation function 의 약어 = sigmoid'logistic'가 default 임
# linear.output=F 출력노드를 activation 안함 (만약 T이면, 회귀분석)
nn1<-neuralnet(RESPOND~AGE+FICO+BUY18, data=train, hidden=3,
stepmax = 1e+04, threshold = 0.01, act.fct='logistic', linear.output=F) 
summary(nn1)
print(nn1$weights)
head(nn1$net.result[[1]])
plot(nn1)
```

```{r}
# hidden=c(3,3) 은닉층은 2개, 층마다 3개의 은닉노드 
set.seed(1234)
nn2<-neuralnet(RESPOND~AGE+FICO+BUY18,data=train, hidden=c(3,3),
stepmax = 1e+04, threshold = 0.01, act.fct='logistic', linear.output=F) 
plot(nn2)
```

```{r}
pred1<-compute(nn1,covariate=test[,c("AGE","FICO","BUY18")])  ## 예측치
head(pred1$net.result,10)
pred2<-compute(nn2,covariate=test[,c("AGE","FICO","BUY18")])  ## 예측치
head(pred2$net.result,10)

library(pROC)
roccurve1 <- roc(test$RESPOND ~ as.vector(pred1$net.result))
plot(roccurve1)
auc(roccurve1)
roccurve2 <- roc(test$RESPOND ~ as.vector(pred2$net.result))
plot(roccurve2)
auc(roccurve2)

logit1 = glm(RESPOND~AGE+FICO+BUY18,family=binomial(),data=train)
prob_pred1 = predict(logit1, newdata=test, type='response') ## predicted probability
roccurve3 <- roc(test$RESPOND ~ prob_pred1)
plot(roccurve3)
auc(roccurve3)

```